\papertitle

### 2017-03-23 article-icmc2017.tex
work

\begin{figure}[h]
  \centering
  \includegraphics[width=0.35\textwidth]{images/iscore-example.eps}
  \caption{Part of an i-score scenario, showcasing the temporal syntax used. 
    A full horizontal line means that the time must not be interrupted, 
    while a dashed horizontal line means that the time of this time constraint can be interrupted to proceed 
  to the following parts of the score according to an external event.}
  \label{fig.iscore-example}
\end{figure}

@@

Throughout this paper, we will use the execution traces in fig.~\ref{fig.simple} and fig.~\ref{fig.simple-reversed} as running example.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[scale=0.5]
    \draw[line width=2pt] (0, 0) rectangle (5, 2);
    \draw[line width=2pt] (0 + 3, 0 - 2.5) rectangle (5 + 3, 2 - 2.5);

    \draw[line width=2pt] 
    (0, -3.75) -- 
    (0, -4) -- (3, -4) -- 
    (3, -3.75) --
    (3, -4) -- (5, -4) -- 
    (5, -3.75) -- 
    (5, -4) -- (8, -4) -- 
    (8, -3.75);

    \node (t1) at (1.45, -3.45) {\large $t_0$};
    \node (t2) at (4, -3.45) {\large $t_1$};
    \node (t3) at (6.5, -3.45) {\large $t_2$};

    \node (f1) at (2.5, 1) {\large $f_1$} ;
    \node (f2) at (5.5, -1.5) {\large $f_2$} ;
  \end{tikzpicture}
  \caption{A possible trace of execution for two processes}
  \label{fig.simple}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}[scale=0.5]

    \draw[line width=2pt] (0 + 3, 0) rectangle (5 + 3, 2);
    \draw[line width=2pt] (0, 0 - 2.5) rectangle (5, 2 - 2.5);

    \draw[line width=2pt] 
    (0, -3.75) -- 
    (0, -4) -- (3, -4) -- 
    (3, -3.75) --
    (3, -4) -- (5, -4) -- 
    (5, -3.75) -- 
    (5, -4) -- (8, -4) -- 
    (8, -3.75);

    \node (t1) at (1.45, -3.45) {\large $t_0$};
    \node (t2) at (4, -3.45) {\large $t_1$};
    \node (t3) at (6.5, -3.45) {\large $t_2$};

    \node (f1) at (5.5, 1) {\large $f_1$} ;
    \node (f2) at (2.5, -1.5) {\large $f_2$} ;
  \end{tikzpicture}
  \caption{Another trace of execution with the same processes}
  \label{fig.simple-reversed}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}[scale=0.5]
	 \node[draw, circle] (f1) at (0, 0) { $f_1$ };
	 \node[draw, circle] (f2) at (3, 0) { $f_2$ }
	    edge [<-] (f1);
	\end{tikzpicture}
	\caption{Another trace of execution with the same processes}
	\label{fig.simple-reversed}
\end{figure}

@@

During a tick, adresses have access to two sets of values: 
\begin{itemize}
  \item The values that were in the environment at the beginning of the tick.
  \item The values produced by previous implicit output ports in the dataflow.
        Section~\ref{sec.relationships} presents the various policies that nodes can leverage to 
        use these values.
\end{itemize}

Let $\mathrm{ticks}$ be the function that gives the number of ticks in an interval.+
For a given execution following fig.~\ref{fig.simple}, the evolution of such parameters may look like :

\begin{table}
	\centering
	\begin{tabular}{c|ccc}
		Address & $t_0$ & $t_1$ & $t_2$ \\
		\midrule
		Global \lstinline|/a|  & $x$ & $x $ & \\
		Local \lstinline|/a|   & $\emptyset$ & & \\	
	\end{tabular}
	\caption{}
\end{table}

@@

\subsection{In the cables}
The most precise way to set-up dependency-related information would be in 
the cables connecting two ports.

@@

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.35\textwidth]{images/iscore-example.eps}
  \caption{Part of an OSSIA scenario, showcasing the temporal syntax used. 
    A full horizontal line means that the time must not be interrupted, 
    while a dashed horizontal line means that the time of this time constraint can be interrupted to proceed 
  to the following parts of the score according to an external event.}
  \label{fig.iscore-example}
\end{figure}

@@

Throughout this paper, we will use the execution traces in fig.~\ref{fig.simple} and fig.~\ref{fig.simple-reversed} as running example, as well as the relationships between $f_1$ and $f_2$ present in fig.~\ref{fig.simple-dataflow}.

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.16\textwidth}\centering
		\begin{tikzpicture}[scale=0.5]
		\node[draw, circle] (f1) at (0, 0) { $f_1$ };
		\node[draw, circle] (f2) at (3, 0) { $f_2$ }
		edge [<-] (f1);
		\end{tikzpicture}\caption{}\label{fig.f1tof2}
	\end{subfigure}~
	\begin{subfigure}{0.16\textwidth}\centering	
		\begin{tikzpicture}[scale=0.5]
		\node[draw, circle] (f1) at (0, 0) { $f_1$ };
		\node[draw, circle] (f2) at (3, 0) { $f_2$ }
		edge [->] (f1);
		\end{tikzpicture}\caption{}
	\end{subfigure}~	
	\begin{subfigure}{0.16\textwidth}\centering
		\begin{tikzpicture}[scale=0.5]
		\node[draw, circle] (f1) at (0, 0) { $f_1$ };
		\node[draw, circle] (f2) at (3, 0) { $f_2$ };
		\end{tikzpicture}\caption{}
	\end{subfigure}
	\caption{Possible dataflows between $f_1$ and $f_2$}
	\label{fig.simple-dataflow}
\end{figure}

    \begin{figure}
    	\centering
\begin{subfigure}{0.25\textwidth}
  \centering
  \begin{tikzpicture}[scale=0.25]
    \draw[] (0, 0) rectangle (5, 2);
    \draw[] (0 + 3, 0 - 2.5) rectangle (5 + 3, 2 - 2.5);

    \draw[] 
    (0, -3.75) -- 
    (0, -4) -- (3, -4) -- 
    (3, -3.75) --
    (3, -4) -- (5, -4) -- 
    (5, -3.75) -- 
    (5, -4) -- (8, -4) -- 
    (8, -3.75);

    \node (t1) at (1.45, -3.45) {\footnotesize $t_0$};
    \node (t2) at (4, -3.45) {\footnotesize $t_1$};
    \node (t3) at (6.5, -3.45) {\footnotesize $t_2$};

    \node (f1) at (2.5, 1) {\footnotesize $f_1$} ;
    \node (f2) at (5.5, -1.5) {\footnotesize $f_2$} ;
  \end{tikzpicture}
  \caption{A possible trace of execution for $f_1$ and $f_2$}
  \label{fig.simple}
\end{subfigure}~	
\begin{subfigure}{0.25\textwidth}
  \centering
  \begin{tikzpicture}[scale=0.25]

    \draw[] (0 + 3, 0) rectangle (5 + 3, 2);
    \draw[] (0, 0 - 2.5) rectangle (5, 2 - 2.5);

    \draw[] 
    (0, -3.75) -- 
    (0, -4) -- (3, -4) -- 
    (3, -3.75) --
    (3, -4) -- (5, -4) -- 
    (5, -3.75) -- 
    (5, -4) -- (8, -4) -- 
    (8, -3.75);

    \node (t1) at (1.45, -3.45) {\footnotesize $t_0$};
    \node (t2) at (4, -3.45) {\footnotesize $t_1$};
    \node (t3) at (6.5, -3.45) {\footnotesize $t_2$};

    \node (f1) at (5.5, 1) {\footnotesize $f_1$} ;
    \node (f2) at (2.5, -1.5) {\footnotesize $f_2$} ;
  \end{tikzpicture}
  \caption{Another trace of execution}
  \label{fig.simple-reversed}
\end{subfigure}
\caption{Process activation traces}
\end{figure}

@@

During a tick, adresses have access to two sets of values, corresponding to scopes: 
\begin{itemize}
  \item The values that were in the environment at the beginning of the tick.
  \item The values produced by previous implicit output ports in the dataflow.
        Section~\ref{sec.relationships} presents the various policies that nodes can leverage to 
        use these values. 
        These values are committed to the environment at the end of a tick.
\end{itemize}

For a given execution following fig.~\ref{fig.f1tof2}, the evolution of such parameters would behave as in table~\ref{tbl.evolution}.

\begin{table}[h]
	\centering
	\footnotesize
	\begin{tabular}{c|cccc}
		Address & Before $f_1$ & After $f_1$ & After $f_2$ & Next tick \\
		\midrule
		Global \lstinline|/a|  & $a_0$ & $a_0$ & $a_0$ & $f2(f1(a_0))$\\
		Local \lstinline|/a|   & $\emptyset$ & $f_1(a_0)$ & $f2(f1(a_0))$ & $\emptyset$ \\	
	\end{tabular}
	\caption{Evolution of a parameter in the global and local scope}
	\label{tbl.evolution}
\end{table}

@@

\subsection{In the cables between ports}
The most precise way to set-up dependency-related information would be in 
the cables connecting two ports.

@@

\subsection{In the edges between nodes}
